Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-05 docs/evol.tex
Improved description.

To examine the relation between the persistence of different kinds of
bugs, and of security bugs in particular, we used as a persistence
indicator the number of versions a bug remains open in a project. We
grouped the persistence numbers by bug categories and then performed
both descriptive statistics and a Mann-Whitney U test among all bug
category pairs. The results are presented in
Table~\ref{tbl:bug_persistence}. Cells in brackets show pairs where no
statistically significant difference was found.

@@

\begin{landscape}
  \begin{table}
    \centering
    \caption{Bug Persistence Comparison}
    \label{tbl:bug_persistence}
    \input{bug_persistence.tex}
  \end{table}
\end{landscape}

>>>>

To examine the relation between the persistence of different kinds of
bugs, and of security bugs in particular, we used as a persistence
indicator the number of versions a bug remains open in a project. We
grouped the persistence numbers by bug categories and then performed a
Mann-Whitney $U$ test among all bug category pairs. The results are
presented in Table~\ref{tbl:bug_persistence}. Cells in brackets show
pairs where no statistically significant difference was found.

@@

\begin{landscape}
  \begin{table}
    \caption{Bug Persistence Comparison}
    \label{tbl:bug_persistence}
    \input{bug_persistence.tex}
    \small The matrix presents pairwise Mann-Whitney $U$ test results
    between the different bug categories. Each cell contains the test
    result (the value of $U$), the $p$-value, the average for each
    category and the sample size for each category. Cells in brackets show
    pairs where no statistically significant difference was found.
  \end{table}
\end{landscape}
